Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-14 paper/paper.tex
nudges

%\red{[The following description can be made shorter, crisper?]}

The synthesis process is illustrated in Fig.~\ref{DSVerifier_process}. 
A~detailed description of DSVerifier tool can be found
in~\cite{IsmailBCFF15}.  Steps $1$ to $3$ are performed by the
user/synthesiser and Steps~A to D are automatically performed by DSVerifier.
%
%, which accepts the
%digital controller transfer functions together with the plant model.  For
%any digital controller, implementation details should be provided ({\it
%e.g.}, number of bits, realization, and sample time).

\begin{figure*}[t]
\centering
\includegraphics[width=\textwidth]{figures/verification-flow.png}
\vspace{1ex}
\caption{Overview of the synthesis process\label{DSVerifier_process}}
\end{figure*}

@@

Given a model for a plant for which to synthesise a controller, provided in
an ANSI-C code input file (Steps 1-3), DSVerifier constructs a
non-deterministic model to represent the plant family (Step A), and
formulates a function (step B) using implementation details provided from
Step $2$ and $3$ to calculate the parameters of the controller to be
synthesised (step C).  Finally DSVerifier builds an intermediate ANSI-C code
for the digital system implementation, which is used as input for the
controller synthesiser (Step D).

This intermediate ANSI-C code model contains a specification $\phi$ for the
verification properties ({\it i.e.}, robust stability) and is provided to
CBMC's~\cite{ClarkeKL04} integrated Counterexample-Guided Inductive
Synthesis (CEGIS) module, where the controller is marked as input variable
to synthesise.  The properties specified in the ANSI-C code model can only
be satisfied if CEGIS synthesises controller coefficients satisfying $\phi$. 
CEGIS employs an iterative, counterexample-guided refinement process which
is explained in detail in section~\ref{synthesiser-general}.  A successful
synthesis result is reported if CEGIS generates a controller which is safe
with respect to $\phi$.  In particular, the ANSI-C code model guarantees
that a synthesised solution is complete and sound with respect to stability
property $\phi$, since it does not depend on system inputs and outputs.  In
the case of stability, the specification $\phi$ consists in a number of
assumptions on the polynomial coefficients, following Jury's Criteria, as
well as the restrictions set in the representation of these coefficients.

@@

In order to synthesise closed-loop digital control systems, we use a program
synthesis engine.  Nowadays, such engines are used increasingly often in
program verification~\cite{DBLP:conf/lpar/DavidKL15, DBLP:conf/cav/0001A14}. 
Our program synthesiser makes use of Counter-Example Guided Inductive
Synthesis (CEGIS) \cite{sketch}.  We start by presenting its general
architecture followed by describing the parts specific to closed-loop
control systems.

>>>>

In order to synthesise closed-loop digital control systems, we use a program
synthesis engine.  Our program synthesiser implements Counter-Example Guided
Inductive Synthesis (CEGIS)~\cite{sketch}.  We start by presenting its
general architecture followed by describing the parts specific to
closed-loop control systems.  A high-level view of the synthesis process is
given in Fig.~\ref{DSSynth_process}.  Steps $1$ to $3$ are performed by
the user and Steps~A to D are automatically performed by our tool for
Digital Systems Synthsis, named DSSynth.
%
%, which accepts the
%digital controller transfer functions together with the plant model.  For
%any digital controller, implementation details should be provided ({\it
%e.g.}, number of bits, realization, and sample time).

\begin{figure*}[t]
\centering
\includegraphics[width=\textwidth]{figures/verification-flow.png}
\vspace{1ex}
\caption{Overview of the synthesis process\label{DSSynth_process}}
\end{figure*}

@@

Given a model for a plant for which to synthesise a controller, provided in
an ANSI-C input file (Steps 1--3), DSSynth constructs a non-deterministic
model to represent the plant family (Step~A), and formulates a function
(step~B) using implementation details provided in Steps~$2$ and $3$ to
calculate the parameters of the controller to be synthesised (Step~C). 
Finally, DSSynth builds an intermediate ANSI-C code for the digital system
implementation, which is used as input for the CEGIS engine (Step~D).

This intermediate ANSI-C code model contains a specification $\phi$ for the
property of interst (i.e., robust stability) and is passed to
CBMC's~\cite{ClarkeKL04} integrated Counterexample-Guided Inductive
Synthesis (CEGIS) module, where the controller is marked as input variable
to synthesise.  The properties specified in the ANSI-C code model can only
be satisfied if CEGIS synthesises controller coefficients that
satisfy~$\phi$.  CEGIS employs an iterative, counterexample-guided
refinement process which is explained in detail in
section~\ref{synthesiser-general}.  A successful synthesis result is
reported if CEGIS generates a controllerthat is safe with respect to~$\phi$. 
In particular, the ANSI-C code model guarantees that a synthesised solution
is complete and sound with respect to stability property~$\phi$, since it
does not depend on system inputs and outputs.  In the case of stability, the
specification~$\phi$ consists in a number of assumptions on the polynomial
coefficients, following Jury's Criteria, as well as the restrictions set in
the representation of these coefficients.

@@
